---
title: "Supplementary information: Adaptation to melanopic stimulation does not affect cone-mediated flicker sensitivity"
output:
  pdf_document: default
  word_document: default
---
```{r, echo = FALSE, include = FALSE}

source('Abstract_VSS_2019.analysis.R')
```

```{r plot_JNDs, echo=FALSE, dev='pdf'}
JNDs %>% 
  # Convert back to tall: separate rows for high/low
  gather(low,high,key='adaptationLevel',value='JND') %>%
  mutate(adaptationLevel=factor(adaptationLevel,levels=c('low','high'))) %>%

  # Plot
  ggplot() +
  aes(x = adaptationLevel, y = JND) +
  facet_grid(participant ~ axis) +
  ylab("LMS Threshold") +
  xlab("Adaptation level") +
  theme_bw() +
  
  # Individual sessions
  geom_line(aes(group=session), alpha = .4) +

  # # Medians over sessions
  # stat_summary(aes(group=1),
  #              fun.y = median,
  #              size = 1,
  #              geom = "line",
  #              na.rm=TRUE) +
  
  # Point ranges median +- SEM(edian)
  geom_pointrange(stat="summary",
                fun.y = median,
                fun.ymin = medianMinusSEM,
                fun.ymax = medianPlusSEM,
                na.rm=TRUE)
```

Threshold for detection of LMS flicker, expressed as the mean change in LMS excitation across L, M, and S-cone photoreceptors. Thresholds are normalized to each participant's median (across sessions) threshold on the low backgrounds (separately for melanopsin and LMS background pairs). Points indicate median across sessions; lines show thresholds obtained in the same experimental session.  Error bars indicate +/-1 standard error of the median.