---
title: "Validations Summary"
params:
  csvsPath: ../../data/processed
output:
  pdf_document: default
  html_notebook: default
---
```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(stringr)
library(grid)
source('../lib/median_SEM.R')
knitr::opts_chunk$set(fig.width=10, fig.height=8) 
```

We validate the background luminances, the background-pair (hi vs. low) contrast, and the flicker contrast for the flicker direction on each background at nominally 5%. These are in files named `luminancesBackgrounds.csv`,`contrastsBackgrounds.csv`, and `contrastsFlicker.csv`, respectively, for each session -- each session being a `$PARTICIPANT/$SESSION/` subdirectory. We read in all of these, and concatenate into a single dataframe per validation-type.
```{r merge, echo=FALSE}
csvsPath = normalizePath(params$csvsPath)

luminancesBackgroundsFiles = list.files(csvsPath, recursive = TRUE, pattern = 'luminancesBackgrounds\\.csv')
luminancesBackgrounds = lapply(luminancesBackgroundsFiles,function(x) {
  read_csv(file.path(csvsPath,x), col_types = cols())
}) %>%
  bind_rows

contrastsBackgroundsFiles = list.files(csvsPath, recursive = TRUE, pattern = 'contrastsBackgrounds\\.csv')
contrastsBackgrounds = lapply(contrastsBackgroundsFiles,function(x) {
  read_csv(file.path(csvsPath,x), col_types = cols())
}) %>%
  bind_rows

contrastsFlickerFiles = list.files(csvsPath, recursive = TRUE, pattern = 'contrastsFlicker\\.csv')
contrastsFlicker = lapply(contrastsFlickerFiles,function(x) {
  read_csv(file.path(csvsPath,x), col_types = cols())
}) %>%
  bind_rows

contrastsFlicker = contrastsFlicker %>%
  spread(receptor,contrast)
```
```{r postreceptorals, echo=FALSE}
contrastsBackgrounds = contrastsBackgrounds %>%
  mutate(LMS = (L+M+S)/3) %>%
  mutate(SminusLplusM = S-.5*(L+M)) %>%
  mutate(LminusM = L-M)

contrastsFlicker = contrastsFlicker %>%
  mutate(LMS = (L+M+S)/3) %>%
  mutate(SminusLplusM = S-.5*(L+M)) %>%
  mutate(LminusM = L-M)
```
```{r filter_out_preCorrecton, echo = FALSE}
luminancesBackgrounds = luminancesBackgrounds %>% filter(label != 'PreCorrection') %>% mutate(label = str_replace(label,'PostCorrection','PreSession'))
contrastsBackgrounds = contrastsBackgrounds %>% filter(label != 'PreCorrection') %>% mutate(label = str_replace(label,'PostCorrection','PreSession'))
contrastsFlicker = contrastsFlicker %>% filter(label != 'PreCorrection') %>% mutate(label = str_replace(label,'PostCorrection','PreSession')) %>% mutate(direction = str_replace(direction,'FlickerDirection_',''))
```

# Backgrounds
```{r luminancesBackgrounds, echo=FALSE}
luminancesBackgrounds %>% 
  mutate(sessionName = str_replace(sessionName,'session_','')) %>%
  group_by(participant,sessionName,label,direction) %>%
  summarise(luminance = median(lumActual)) %>%
  group_by(participant,sessionName,direction) %>%
  spread(key = label, value = luminance) %>%
  ggplot() +
    geom_segment(aes(x = sessionName, xend = sessionName, y = PreSession, yend = PostSession), arrow = arrow(length = unit(0.03, "npc"))) +
    ylab('Measured luminance (cd/m^2)') +
    xlab('session') +
    ggtitle('Background luminances') +
    theme_bw() +
    facet_grid(participant ~ direction)
```
First, we plot the measured luminance of each of the backgrounds. In this figure, each panel is one background-type (`LMS/Mel` `high/low`), for one participant. In each panel, there is 1 arrow per session, pointing from the pre-experiment (post-correction) measured luminance, to the post-experiment measured luminance.

```{r contrastBackgrounds, echo = FALSE}
contrastsBackgrounds %>%
  group_by(participant,sessionName,label,axis) %>%
  summarise(LMS = median(LMS),
            Mel = median(Mel)) %>%
  ggplot() +
  aes(x = LMS, y = Mel, color = label, shape = axis) +
  geom_point(alpha = .8) +
  scale_y_continuous(breaks = seq(0,400,50)) +
  scale_x_continuous(breaks = seq(0,400,50)) +
  coord_equal(ratio=1) +  
  ylab('Melanopsin contrast (%)') +
  xlab('LMS contrast (%)') +  
  ggtitle('Background pair contrasts') +
  geom_vline(xintercept = 350, alpha = .5, linetype='dashed') +
  geom_hline(yintercept = 350, alpha = .5, linetype='dashed') +
  theme_bw()
```

Here we plot the photoreceptor contrast (calculated from measured spectral power distribution) for each background-pair (`LMS`-directed and `Mel`-directed). Each datapoint in the figure is the photoreceptor contrast increase when going from the `low` to the `high` background of that pair; nominal target is 350%. Colors indicate pre- and post-session measurements, and symbols indicate different background-pair.
\pagebreak

# Flicker contrast
```{r contrastsFlicker, echo = FALSE}
pLM = contrastsFlicker %>%
  group_by(participant,sessionName,label,direction,component) %>%
  summarise(LMS = median(LMS), LminusM = median(LminusM)) %>%
  ggplot() +
  aes(x = LMS, y = LminusM, color = label) +
  geom_point(stat = 'identity',alpha = .5) +
  scale_y_continuous(labels = scales::percent, limits=c(-.07,.07), breaks = seq(-.07,.07,.02)) +
  scale_x_continuous(labels = scales::percent, limits=c(-.07,.07), breaks = seq(-.07,.07,.02)) +
  ylab('L-M contrast') +
  xlab('') +
  ggtitle('Flicker contrasts') +
  coord_equal(ratio=1) +
  geom_hline(yintercept = 0, alpha = .5) +
  geom_vline(xintercept = 0, alpha = .5) +
  geom_vline(xintercept = .05, alpha = .5, linetype='dashed') +
  geom_vline(xintercept = -.05, alpha = .5, linetype='dashed') +
  theme_bw() + theme(legend.position = "none") +
  facet_grid(~ direction)
```
```{r contrastsFlicker_S, echo = FALSE}
pS = contrastsFlicker %>%
  group_by(participant,sessionName,label,direction,component) %>%
  summarise(LMS = median(LMS), S = median(SminusLplusM)) %>%
  ggplot() +
  aes(x = LMS, y = S, color = label) +
  geom_point(stat = 'identity',alpha = .5) +
  scale_y_continuous(labels = scales::percent, limits=c(-.08,.08), breaks = seq(-.09,.09,.02)) +
  scale_x_continuous(labels = scales::percent, limits=c(-.07,.07), breaks = seq(-.07,.07,.02)) +
  ylab(expression(paste("S - ", frac('L+M', 2)))) +
  xlab('LMS contrast') +
  coord_equal(ratio=1) +
  geom_hline(yintercept = 0, alpha = .5) +
  geom_vline(xintercept = 0, alpha = .5) +
  geom_vline(xintercept = .05, alpha = .5, linetype='dashed') +
  geom_vline(xintercept = -.05, alpha = .5, linetype='dashed') +
  theme_bw() + theme(legend.position = "bottom") +
  facet_grid(~ direction)
```
```{r contrastsFlicker_combine, echo = FALSE}
grid.newpage()
grid.draw(rbind(ggplotGrob(pLM), ggplotGrob(pS), size = "last"))
```

Here we plot the photoreceptor contrast of the flicker directions, one for each background-type (`LMS/Mel` `high/low`), at nominally 5% `LMS` contrast. In the first row of panel, the contrast on the `L-M` postreceptoral channel is graphed vertically; the second row of panels plots the contrast on the S-cone compared to the average of the L- and M-cones (`S-.5*(L+M)`) vertically. In both rows, the horizontal position indicates the `LMS` contrast as the mean of the L-, M-, and S-cone contrasts. Color indicates whether datapoint is based on measurements made pre-session or post-session.